---
title: "Sentiment Analysis on Tech-based Stocks"
subtitle: "Proposal"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
editor: visual
code-annotations: hover
categories: 
  - Data Mining and Discovery
execute:
  warning: false
---

```{r load_pkgs, message=FALSE, output=FALSE}
# GETTING THE LIBRARIES
if (!require(pacman))
  install.packages(pacman)

pacman::p_load(tidyverse,
               formattable,
               janitor,
               dlookr,
               here)
```

## Dataset

```{r}
#| label: load-dataset
#| message: false
```

A brief description of your dataset including its provenance, dimensions, etc. as well as the reason why you chose this dataset.

Make sure to load the data and use inline code for some of this information.

## Questions

Question 1: Does the world of news headlines influence the intricate dance of stock prices? Can we unveil the secrets?
The question frames the investigation into the influence of new headlines on the stock prices in captivating and
thought-provoking manner. It not only acknowledges the impact of news but also suggests the possibility of
uncovering hidden patterns or insights, which can be appealing to those interested in financial markets and data
analysis.
To address the question in a general sense, we would employ a combination of data analysis and predictive modeling.
By collecting historical data on stock prices and news headlines, we can examine the historical relationship between
news sentiment and market movements. This analysis might involve quantifying sentiment in news headlines,
identifying patterns, and exploring correlations. Furthermore, predictive models can be developed to forecast
potential future stock price changes based on these insights. The goal is to gain a better understanding of how
news impacts stock prices and, if possible, use this knowledge to make informed predictions about future market
behavior.

Question 2: To what extent do changes in the stock prices influence the price movements of other stocks in a particular sector?

We chose this question because it is crucial in the world of finance. It affects how we manage risks, make investments in 
different things, understand industries, create smart trading plans, and make decisions as investors. When stocks in one industry 
move in the same way, it can mean more risk and less benefit from spreading out our investments. On the other hand, when they don't 
move the same way, it can be a chance to lower risk and improve our investments. By figuring out these connections, we can make 
smarter choices about where to invest our money, reduce risks, get a better grip on how industries work, and plan our trading and 
investments more effectively.


## Analysis plan

Variables Involved:

- News Headlines: Collecting a dataset of news headlines relevant to the stock market. These headlines will serve as a variable to assess the impact on stock prices.

- Stock Prices: Gathering historical stock price data for a selected set of stocks within a particular sector. These will be the stocks to study for correlations.

Sector Information: Identifying and categorizing stocks into their respective sectors for sector specific analysis.

Variables to be Created:

- Correlation Coefficients: Calculating the correlation coefficients to quantify the relationships between stock price movements and news headlines, and between stocks within the same sector.

- Market Sentiment Index: Creating a sentiment index based on the tone of the news headlines (positive, negative, or neutral sentiment) to gauge how news sentiment affects stock prices.


Plan Summary:

- We will collect the stock price data and news headlines data.

- Categorize the stocks into sectors.

- To answer question 1, we will calculate correlation coefficients between stock prices and news sentiment .

- To answer question 2, we will calculate correlation coefficients between stock prices of the selected sector.

- And finally, create a sentiment index to gauge news sentiment's influence on stock prices.

- We may use external data like economic indicators or sector-specific data like industry specific news or performance metrics.

