---
title: "Sentiment Analysis on Tech-based Stocks"
subtitle: "Proposal"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
editor: visual
code-annotations: hover
categories: 
  - Data Mining and Discovery
execute:
  warning: false
---

```{r load_pkgs, message=FALSE, output=FALSE}
# GETTING THE LIBRARIES
if (!require(pacman))
  install.packages(pacman)

pacman::p_load(tidyverse,
               formattable,
               janitor,
               dlookr,
               here)
```
## Introduction

Our aim is to develop a robust stock prediction model by analyzing the correlation between news sentiment and market movements, while also exploring the interconnected dynamics of stock prices within specific sectors.

## Abstract

Our primary objective is to develop an advanced predictive model using the `yahoofinance` package, meticulously tailored for stock analysis, with Apple Inc. (AAPL) serving as a prominent example. This model is intricately designed to unravel the nuanced correlation between news sentiment and the dynamic landscape of stock prices. Leveraging sophisticated methodologies in natural language processing and machine learning, our goal is to discern identifiable patterns and trends within news data, providing invaluable insights into their profound impact on the pricing dynamics of stocks, illustrated by the case of `AAPL`. This predictive framework is meticulously crafted not only to forecast individual movements in example stocks with precision but also to contribute to a thorough understanding of the profound influence exerted by news sentiment on market behaviors, specifically within the technology sector.

In addition, our focus extends to the exploration of the intricate network of interdependencies among stocks within the technology sector. A pivotal aspect of our objectives involves scrutinizing how fluctuations in the stock prices of one entity can act as a catalyst, triggering substantial market responses in others within the sector. Obtaining in-depth insights into how shifts in the stock prices of one company, notably Apple Inc., can propagate influence throughout the sector is crucial for informing strategic decision-making and anticipating broader market dynamics within the industry. This exploration not only augments our predictive accuracy but also furnishes strategic decision-makers with invaluable insights for informed decision-making.

## Dataset

```{r}
#| label: load-dataset
#| message: false
```

A brief description of your dataset including its provenance, dimensions, etc. as well as the reason why you chose this dataset.

Make sure to load the data and use inline code for some of this information.

## Questions

The two questions you want to answer.

## Analysis plan

|               Week                | Weekly Tasks                                                                          | Persons in Charge |  Backup  |
|:----------------:|-------------------|:----------------:|:----------------:|
|       until November 8^th^        | Explore and finalize the dataset and the problem statements                           |     Everyone      | Everyone |
|                \-                 | Complete the proposal and assign some high-level tasks                                |     Everyone      | Everyone |
|     November 9^th^ to 15^th^      | Getting to know about `yfinance` library                                              |        TBD        |   TBD    |
|                \-                 | Data cleaning and Data pre-processing                                                 |        TBD        |   TBD    |
|                \-                 | Question specific exploration and data categorization                                 |        TBD        |   TBD    |
|     November 16^th^ to 22^nd^     | Performing Sentiment analysis for Q1                                                  |        TBD        |   TBD    |
|                \-                 | Performing Sentiment analysis for Q2                                                  |        TBD        |   TBD    |
|                \-                 | Exploring on how to integrate our analysis with real-time prices.                     |        TBD        |   TBD    |
|     November 23^rd^ to 29^th^     | Generating remaining parts of the plots for Q1 and Q2                                 |        TBD        |   TBD    |
|                \-                 | Improving the generated sentiment analysis  model                                     |        TBD        |   TBD    |
|                \-                 | Start integrating quarto and our model                                                |        TBD        |   TBD    |
| November 30^th^ to December 6^th^ | Refining the code for code review with comments                                       |        TBD        |   TBD    |
|                \-                 | Making a few changes on the model to test it based on historical data                 |        TBD        |   TBD    |
|                \-                 | Continue with the integration of quarto and our models                                |        TBD        |   TBD    |
|     December 7^th^ to 13^th^      | Complete the quarto website with presentable data                                     |        TBD        |   TBD    |
|                \-                 | Review the model and debugging                                                        |        TBD        |   TBD    |
|                \-                 | Write-up and presentation for the project                                             |     Everyone      | Everyone |

: {.hover}

### Repo Organization

The following are the folders involved in the Project repository.

-   **'data/':** Used for storing any necessary data files for the project, such as input files.

-   **'images/':** Used for storing image files used in the project.

-   **'\_extra/':** Used to brainstorm our analysis which won't impact our project workflow.

-   **'\_freeze/':** This folder is used to store the generated files during the build process. These files represent the frozen state of the website at a specific point in time.

-   **'.github/':** Folder for storing github templates and workflow.


::: callout-note
## Note:

These are the planned approaches, and we intend to explore and solve the problem statement which we came up with. Parts of our approach might change in the final implementation.
:::

